Uncertainty on the galaxy-halo connection for Lyman-$\alpha$ emitters at $z=3.1$

### 2016-03-21 paper/ms.tex
nueva version del plot 1

\begin{figure}
\includegraphics[width=0.46\textwidth, height=0.38\textwidth]{ndist.png}
\caption{Cumulative halo number distribution function over the 27 mock fields of the simulation for different models of $M_{\rm min}$-$M_{\rm max}$.}
\label{fig:cosmicv0}
\end{figure}

@@

\begin{figure*}
\includegraphics[width=0.99\textwidth]{likelyplot_1deg_total.png}
%\includegraphics[width=0.47\textwidth]{likelyplot_1degf.png}
%\includegraphics[width=0.47\textwidth]{likelyplot_1degdM.png}
%\includegraphics[width=0.47\textwidth]{likelyplot_1degdMf.png}
\caption{One and two dimensional projections of the posterior probability distributions of \mmin, \mmax and \focc as described in the label of each sub-figure.}
\label{fig:like}
\end{figure*}

>>>>

\begin{figure}
\includegraphics[width=0.50\textwidth]{fig1.pdf}
\caption{Cumulative halo number density distribution function over
  27 mock fields. Each line corresponds to a
  different model with increasig values of $M_{\rm min}$. 
  Different models produce different number density distributions. The
width increases with \mmin.} 
\label{fig:cosmicv0}
\end{figure}

@@

\begin{figure*}
\begin{center}
\includegraphics[width=0.85\textwidth]{likelyplot_1deg_total.png}
\end{center}
\caption{One and two dimensional projections of the posterior
  probability distributions of \mmin, \mmax and \focc as described in
  the label of each sub-figure.} 
\label{fig:like}
\end{figure*}
